Component response rate variation underlies the stability of complex systems

### 2020-03-08 notebook/ms.Rmd
Remove a bit of the notes to myself, as the sections are now more or less clear

umerical simulations reveal that $\sigma^{2}_{\gamma} > 0$ results in a nonlinear relationship between $\rho$ and $\max(\Re(\lambda))$, which can sometimes increase the stability of the system.

@@

<!--- The current Figure 1 should be replaced by the new figure first shown in revision_notes.Rmd --->

@@

<!--- Here a new section is needed --->
<!---

**Effects of $\gamma$ and correlated interactions on stability**

This is going to require that a new figure be inserted showing correlation versus stability. Some general points about how $rho$ is known to affect stability is also needed, but this should not be too difficult to explain in a sentence or two.

@@

This will report results for small-world, scale-free, and cascade food-webs. It will also briefly mention random predator-prey, mutualist, and competitor networks. These resutls will require a small table, at least.

>>>>

Numerical simulations reveal that $\sigma^{2}_{\gamma} > 0$ results in a nonlinear relationship between $\rho$ and $\max(\Re(\lambda))$, which can sometimes increase the stability of the system.

@@

@@

@@

This will report results for small-world, scale-free, and cascade food-webs. It will also briefly mention random predator-prey, mutualist, and competitor networks. These results will require a small table, at least.
